Target Markdown

### 2022-11-23 _targets.Rmd
pipeline adapted, but doesnt run via targets because it gets stuck on all_authors becuase there are empty fields

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
    #  tar_target(all_pubs,
    #        get_all_pubs(db_path, matching, ids_complete), 
    #           format = "qs"),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector))

@@

    # tar_target(edgelist,
    #            make_edgelist(one_author),
    #             format = "qs", pattern = map(one_author), iteration = "list"),
    # tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")

@@

    # tar_target(eigen_centr,
    #            calc_eigen_centr(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list")
    # 
)

@@

    #  tar_target(clustering,
    #             calc_clustering(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list") 
    # #            
    # # 
)

@@

     # tar_target(ind_pubs,
     #            calc_ind_pubs(one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author),                  iteration = "list")
     # 
)

@@

     # tar_target(ind_topics,
     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author), iteration = "list")
     # 
)

@@

    # tar_target(final_data,
    #            calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
    #            format = "qs") #,
    #  # tar_target(testing,
    #  #           just_test(db_path),
    #  #           format = "qs")
    # 
)

>>>>

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
    #  tar_target(all_pubs,
    #        get_all_pubs(db_path, matching, ids_complete), 
    #           format = "qs"),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector))

@@

    # tar_target(edgelist,
    #            make_edgelist(one_author),
    #             format = "qs", pattern = map(one_author), iteration = "list"),
    # tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")
    tar_target(coauthorship,
               make_network(all_authors)),

     tar_target(coauthorship_graph,
               make_graph(all_authors))

@@

    # tar_target(eigen_centr,
    #            calc_eigen_centr(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list")
    # 
     tar_target(eigen_centrality,
               comp_eigen_centr(coauthorship_graph))

@@

    #  tar_target(clustering,
    #             calc_clustering(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list") 
    # #            
    # #

    tar_target(cluster,
                comp_clustering(eigen_centrality))

@@

     # tar_target(ind_pubs,
     #            calc_ind_pubs(one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author),                  iteration = "list")
     # 
     tar_target(independent_pubs,
                comp_ind_pubs(cluster))
)

@@

     # tar_target(ind_topics,
     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author), iteration = "list")
     # 
    tar_target(independent_topics,
                comp_ind_topics(independent_pubs))
)

@@

    # tar_target(final_data,
    #            calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
    #            format = "qs") #,
    #  # tar_target(testing,
    #  #           just_test(db_path),
    #  #           format = "qs")

    tar_target(full_indicator,
               calc_full_indicator(independent_topics),
